---
title: "Test plots intersex"
author: "DHJ"
date: "20 6 2019"
output: html_document
---

# Test plots of snail intersex  
  
Files and species:  
    - Strandsnegl_intersex_2005_2018.RData  - common periwinkle (Littorina littorea)  
    - Kongsnegl_intersex_2013_2014.RData    - common whelk (Buccinum undatum)   
    - Nettsnegl_intersex_2007_2014.RData    - netted dog whelk (Nassarius reticulatus)  
    - Purpursnegl_intersex_2007_2014.RData  - dog whelk (Nucella lapillus)  

```{r setup}
library(ggplot2)
library(dplyr)
```

## 1. Data
```{r data}
data_strandsnegl <- readRDS("Data/Strandsnegl_intersex_2005_2018.RData")
data_kongsnegl <- readRDS("Data/Kongsnegl_intersex_2013_2014.RData")
data_nettsnegl <- readRDS("Data/Nettsnegl_intersex_2007_2014.RData")
data_purpursnegl <- readRDS("Data/Purpursnegl_intersex_2007_2014.RData")
```

## 2. Plots of common periwinkle (strandsnegl)
### One station, all years
```{r}
station <- "6"
data_strandsnegl %>%
  filter(!is.na(ISI)) %>%
  filter(Station %in% station) %>%
  ggplot(aes(ISI)) + 
  geom_histogram(binwidth = 1) +
  facet_wrap(~Year) +
  labs(title = paste("Common periwinkle, station", station))
  
```

### One year, all stations
```{r}
year <- 2007
data_strandsnegl %>%
  filter(!is.na(ISI)) %>%
  filter(Year %in% year) %>%
  ggplot(aes(ISI)) + 
  geom_histogram(binwidth = 1) +
  facet_wrap(~Station) +
  labs(title = paste("Common periwinkle,", year))
```

### Make summary data
```{r}
# All data, percentages
data_summ_perc <- data_strandsnegl %>%
  filter(!is.na(ISI)) %>%
  group_by(Station, Year) %>%
  mutate(N = n()) %>%
  group_by(Station, Year, ISI) %>%
  summarize(Percent = n()/first(N)*100)
# Test
# data_summ_perc %>%  ilter(Station %in% "6" & Year == 2010) %>% 
#   ggplot(aes(ISI, Percent)) + geom_col() + coord_flip()

# All data, means
data_summ_mean <- data_strandsnegl %>%
  filter(!is.na(ISI)) %>%
  group_by(Station, Year) %>%
  summarize(ISI_mean = mean(ISI), ISI_min = min(ISI), ISI_max = max(ISI))
```

### Plot percentages
```{r, fig.width=9.5}
ggplot(data_summ_perc, aes(ISI, Percent)) +
  geom_col() + 
  coord_flip() +
  facet_grid(Station~Year) +
  theme(axis.text.x = element_text(hjust = 0, angle = -55),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 20), angle = 0, vjust = 0.5, size = 16)) +
  labs(y = "Percent of population", title = "Common periwinkle")
```

### Plot means
```{r}
ggplot(data_summ_mean, aes(Year, ISI_mean)) +
  geom_line() + geom_point() + 
  facet_wrap(~Station) +
  theme(axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 20), angle = 0, vjust = 0.5, size = 16)) +
  labs(y = "mean\nISI", title = "Common periwinkle")

```

common whelk (Buccinum undatum)   
    - Nettsnegl_intersex_2007_2014.RData    - netted dog whelk (Nassarius reticulatus)  
    - Purpursnegl_intersex_2007_2014.RData  - dog whelk (Nucella lapillus) 
    
## 3. Plots of nettsnegl, kongsnegl, purpursnegl
### Make summary data
```{r}
data_3sp <- bind_rows(
  data_kongsnegl %>% mutate(Species = "Common whelk", Species2 = "Bucc und"), 
  data_nettsnegl %>% mutate(Species = "Netted dogwhelk", Species2 = "Nass lap"), 
  data_purpursnegl %>% mutate(Species = "Dogwhelk", Species2 = "Nuce lap")
)

# All data, percentages
data_summ_perc <- data_3sp %>%
  filter(!is.na(stage)) %>%
  group_by(Species2, Station, Year) %>%
  mutate(N = n()) %>%
  group_by(Species2, Station, Year, stage) %>%
  summarize(Percent = n()/first(N)*100)
# Test
# data_summ_perc %>%  ilter(Station %in% "6" & Year == 2010) %>% 
#   ggplot(aes(ISI, Percent)) + geom_col() + coord_flip()

# All data, means
data_summ_mean <- data_3sp %>%
  filter(!is.na(stage)) %>%
  group_by(Species2, Station, Year) %>%
  summarize(ISI_mean = mean(stage), ISI_min = min(stage), ISI_max = max(stage))

```


### Plot percentages
```{r, fig.width=9.5, fig.height=10}
data_summ_perc %>%
  ungroup() %>%
  filter(!(Species2 == "Nuce lap" & Station != "St. 1 Håøya")) %>%
  mutate(Station = ifelse(Species2 == "Nuce lap", "1", Station)) %>%
  mutate(Station = paste("Station", Station)) %>%
  mutate(Species_station = paste0(Station, "\n", Species2)) %>%
ggplot(aes(stage, Percent)) +
  geom_col() + 
  coord_flip() +
  facet_grid(Species_station~Year) +
  theme(axis.text.x = element_text(hjust = 0, angle = -55),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 20), angle = 0, vjust = 0.5, size = 16)) +
  labs(y = "Percent of population", x = "Intersex/\nimposex\nstage", 
       title = "Common periwinkle, netted dogwhelk and dogwhelk")
```


### Plot means
```{r, fig.width=9.5, fig.height=8}
data_summ_mean %>%
  ungroup() %>%
  filter(!(Species2 == "Nuce lap" & Station != "St. 1 Håøya")) %>%
  mutate(Station = ifelse(Species2 == "Nuce lap", "1", Station)) %>%
  mutate(Station = paste("Station", Station)) %>%
  mutate(Species_station = paste0(Station, "\n", Species2)) %>%
ggplot(aes(Year, ISI_mean)) +
  geom_line() + geom_point() + 
  facet_wrap(~Species_station) +
  theme(axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 20), angle = 0, vjust = 0.5, size = 16)) +
  labs(y = "Mean\nIntersex/\nimposex\nstage", title = "Common periwinkle, netted dogwhelk and dogwhelk")

```


