---
title: "Vikkilen, various tables and plots"
author: "DHJ"
date: "24 6 2019"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true  
---

## General  
- percentage sterile females (%S) = (number of sterile females/total number of females)*100
    - stage 2-4 females are sterile
- mean Female Penis Length (FPL)
- mean Male Penis Length (MPL)
For N. lapillus,
- Relative Penis Size Index (RPSI) = (FPL)3/(MPL)3*100 
- imposex index (VDSI) = (sum of the values of imposex stages (ranged 0 to 5) in all females/the number of females collected)  
For B. undatum
- Penis Classification Index (PCI) after Strand and Jacobsen (2002)

## Figures  
- All figures have 'FIG' in the filename (and so can easily be searched)

## Script  
- *This script is a cleaned version of 06_Tables_graphs.Rmd.*  The order of parts 4-6 in this file fits with the order in the MS  

- Figur 7: Er P-verdiene de samme for sedimentene etter at data for 2021 ble inkludert? Hva er prosenten for hele området per år? Vi har ikke noe område 6, så den skal jeg droppe. *Script '07_Sediment_newfile_July2020.Rmd'*   
- Vi droppet figur på TBT-konsentrasjon for blåskjell og strandsnegl, men P var ikke signifikant (P=0,48). Kan du likevel se hva den blir når 2021-dataene er inkludert? Blåskjell skal være en kontroll for strandsnegl, men det gir vel ikke mening hvis det ikke er korrelasjon. *Sections 6 + 8*   
    
    
## 0. Libraries
```{r}
library(dplyr)
library(purrr)    # transpose
library(ggplot2)
library(tidyr)
library(forcats)
library(cowplot)
library(readxl)
library(stringr)

# install.packages("openxlsx")
library(openxlsx)

source("06_Tables_graphs_functions.R")

```

## 0b. Settings
```{r}

save_plots <- TRUE
save_plots <- FALSE

last_year <- 2021

# Back up table (if needed)
if (FALSE){
  
  file.copy("Figures/06_Littorina_tables.xlsx", "Figures/06_Littorina_tables_back_2021-06-21.xlsx")
  
}

```


## 0c. Make 5-color palette  
```{r,fig.height=2}

# library("colorspace") 
# The line below: run it in the Console (bottom window), NOT here (RStudio will hang)
# pal <-choose_palette()

library(pals)

if (FALSE){
  labs=c('alphabet','alphabet2', 'glasbey','kelly','polychrome', 
         'stepped', 'stepped2', 'stepped3', 'tol', 'watlington')
  op=par(mar=c(0,5,3,1))
  pal.bands(alphabet(), alphabet2(), glasbey(), kelly(), polychrome(), 
            stepped(), stepped2(), stepped3(), tol(), watlington(), 
            labels=labs, show.names=FALSE)

  pal.bands(tol(5), glasbey(5), kelly(7)[3:7])
  pal.bands(brewer.blues(4), brewer.reds(4))

  }


station_cols <- c(
  brewer.blues(4)[c(4,3,2)], 
  brewer.reds(6)[c(6,4,2)])
pal.bands(station_cols)

```

## 0d. Station names    
* 'Station_name' mostly used  
* 'Station_name2' used in part 8 ('TBT - all species')    
```{r}

# OLD (before we combined st. 5 and 5b)
st_names <- data.frame(
  Station = c("1", "4", "5", "5b", "6", "7"),
  Station_name = c("St. 1 Håøya, Outer fjord", "St. 4 Hasseldalen", "St. 5 Skjeviga", 
              "St. 5B Båtstø", "St. 6 Shipyard", "St. 7 Inner Vikkilen")
)

# NEW (after combining st. 5 and 5b)
# NOTE: tuis was also changed in the script "06_Tables_graphs_functions.R", used from section 6 onwards
st_names <- data.frame(
  Station = c("71G", "1", "4", 
              "5", "6", "7"),
  Station_name = c("Reference station\nLangesundfjord (100 km)", "Håøya (5.5 km)", "Outer Vikkilen (2.5 km)", 
                   "Skjeviga (0.6 km)", "Shipyard (0 km)", "Inner Vikkilen (0.5 km)"),
  Station_name2 = c("Reference station\nLangesundfjord (100 km)", "Håøya (4-6 km)", "Outer Vikkilen (2 km)", 
                    "Mid Vikkilen (0.8 km)", "Shipyard (0 km)", "Inner Vikkilen (0.5 km)"),
  stringsAsFactors = FALSE
  ) %>%
  mutate(
    Station_name = fct_inorder(Station_name),  # set as factor, for correct order
    Station_name2 = fct_inorder(Station_name2)
  )

# Reverse direction
st_names$Station_name <- factor(st_names$Station_name, 
                                levels = rev(levels(st_names$Station_name)))
st_names$Station_name2 <- factor(st_names$Station_name2, 
                                levels = rev(levels(st_names$Station_name2)))

names(station_cols) <- st_names$Station_name

st_names_mytilus <- tibble::tribble(
    ~Station_Myt, ~Station_name,  ~Station_name2, 
    "b1", "Rivingen (6.4 km)",          "Håøya (4-6 km)", 
    "b2", "Groos (4.0 km)",             "Håøya (4-6 km)",
    "b3", "Grimstadodden (2.4 km)",     "Outer Vikkilen (2 km)",
    "b4", "Biodden (2.1 km)",           "Outer Vikkilen (2 km)",
    "b5", "Kjellviga (1.6 km)" ,        "Outer Vikkilen (2 km)",
    "b6", "Naksbø (1.1 km)",            "Mid Vikkilen (0.8 km)",
    "b7", "Bie (0.8 km)",               "Mid Vikkilen (0.8 km)",
    "b8", "Gjømle/Skjevika (0.6 km)",   "Mid Vikkilen (0.8 km)",
    "b9", "Shipyard (0 km)",            "Shipyard (0 km)", 
    "b10", "Inner Vikkilen (0.5 km)",   "Inner Vikkilen (0.5 km)"
  ) %>%
  mutate(
    Station_name = fct_inorder(Station_name),  # set as factor, for correct order
    Station_name2 = fct_inorder(Station_name2)
  )

```


## 1. Data

### a1. Intersex and TBT raw data  

```{r}

#
# Data made in script 02
#
dat_intersex_litt <- readRDS(file = "Data/02_Strandsnegl_intersex_2005_2018.RData") %>%
  mutate(Station = case_when(Station %in% "St6" ~ "6",
                             TRUE ~ Station),
         Sex = case_when(tolower(Sex) %in% "f" ~ "f",
                         tolower(Sex) %in% "m" ~ "m",
                         TRUE ~ "x")
         )

#
# Data made in script 05
#
dat_tbt <- readRDS(file = "Data/05_TBT.RData")

```


### a2. 2021 Littorina data 
- Fetched from Nivabasen using 5. April 2022, see script 21     
- Littorina TBT added to dat_tbt here
- Mytilus TBT added to dat_tbt in part 8
- Intersex not added here, added to 'dat_intersex_litt_summ' in part 3.c1a

```{r}

dat_2021_biota <- read.csv("Data/21_data_2016-2021_biota.csv")

dat_tbt_2021 <- dat_2021_biota %>%
  filter(MYEAR == 2021,
         LATIN_NAME %in% "Littorina littorea",
         NAME %in% c("Tributyltinn", "Tributyltinn (TBT)")) %>%
  rename(
    Year = MYEAR,
    TBT = VALUE,
    TBT_flag = FLAG1
  ) %>%
  mutate(
    Station = str_extract(STATION_CODE, "[0-9]+"),
    Species = "Littorina"
  ) %>%
  select(Station, Year, Species, TBT, TBT_flag)

cat("dat_tbt_2021:", nrow(dat_tbt_2021), "rows\n")

# Add new data to dat_tbt
check <- dat_tbt$Year == 2021
if (sum(check) == 0){
  dat_tbt <- bind_rows(
    dat_tbt, dat_tbt_2021
  )
  
}

```
### a3. Summarise TBT  

16 April 2020: 
- Combine 5 and 5B

```{r}

# Summarise TBT
dat_tbt_mean <- dat_tbt %>% 
  mutate(Station = case_when(
    Station %in% "5b" ~ "5",
    Station != "5b" ~ Station
  )) %>% # View()
  group_by(Species, Station, Year) %>%
  summarise(TBT_mean = mean(TBT, na.rm = TRUE), TBT_flag = mean(TBT_flag %in% "<"),
            .groups = "drop")

cat("TBT in Littorina, raw data \n")
dat_tbt %>% 
  filter(Station %in% c("1","4","5","5b","6","7") & Species == "Littorina") %>%
  xtabs(~Year + Station, .)
cat("\n")

cat("TBT in Littorina, number of means, 5 and 5B combined \n")
dat_tbt_mean %>% 
  filter(Station %in% c("1","4","5","5b","6","7") & Species == "Littorina") %>%
  xtabs(~Year + Station, .)

# str(dat_tbt_mean)


```



### b. Add station names, snails + sediment only      
Don't include Mytilus (blue mussel, because they use a seperate set of stations, Station_Myt, see script 05)  
```{r}

dat_tbt_mean_snails <- dat_tbt_mean %>%
  filter(!Species %in% "Mytilus") %>%
  left_join(st_names, by = "Station")

str(dat_tbt_mean_snails)

```

### c. Imposex in N. reticulatus (nettsnegl)   

2013 data  
* Supplied later, in a separate file  
```{r, warning=FALSE}

colnames <- c("Nr", "Code", "SH", "AH", 
"Te", "VS", "Pr", "Vd", "Pe_gl", "Gen_excr", "Other_excr", 
"Paras",
"O", "Od", "Ag", "Ig", "Cg", "Vag", "in.Od", "stage", "type", 
"male", "Kommentar")

columntypes <- c(Nr = "numeric", Code = "text", 
                   SH = "numeric", SB = "numeric", yr = "numeric", VS = "text", 
                   Pr = "text", Vd = "text", Pe_gl = "numeric", P_P = "numeric", 
                   Gen_excr = "numeric", Other_excr = "numeric", O = "text", 
                   Od = "text", Ag = "text", Ig = "text", Cg = "text", 
                   Vag = "text", in.Od = "text", stage = "numeric", type = "text", 
                   male = "numeric", Kommentar = "text")


fn <- "Input_data/Nettsnegl-Nassarius-Hinia/imposexskjema 2013_hinia.xls"

sheet <- "7_13"
df_07 <- read_excel(fn, sheet = sheet, range = "A8:W58", 
                    col_names = colnames, col_types = columntypes) %>%
  mutate(Sheet = sheet, 
         Station = "7",
         Year = 2013,
         Nr = as.character(Nr),
         .before = everything())

sheet <- "st6_13"
df_06 <- read_excel(fn, sheet = sheet, range = "A8:W58", 
                    col_names = colnames, col_types = columntypes) %>%
  mutate(Sheet = sheet, 
         Station = "6",
         Year = 2013,
         Nr = as.character(Nr),
         .before = everything())

sheet <- "st5b"
df_05b <- read_excel(fn, sheet = sheet, range = "A8:W58", 
                    col_names = colnames, col_types = columntypes) %>%
  mutate(Sheet = sheet, 
         Station = "5b",
         Year = 2013,
         Nr = as.character(Nr),
         .before = everything())

sheet <- "st5"
df_05 <- read_excel(fn, sheet = sheet, range = "A8:W57", 
                    col_names = colnames, col_types = columntypes) %>%
  mutate(Sheet = sheet, 
         Station = "5",
         Year = 2013,
         Nr = as.character(Nr),
         .before = everything())

sheet <- "st1"
df_01 <- read_excel(fn, sheet = sheet, range = "A8:W57", 
                    col_names = colnames, col_types = columntypes) %>%
  mutate(Sheet = sheet, 
         Station = "1",
         Year = 2013,
         Nr = as.character(Nr),
         .before = everything())

df_2013 <- bind_rows(df_07, df_06, df_05b, df_05, df_01) %>%
  mutate(
    Sex = case_when(
      male %in% 1 ~ "m",
      TRUE ~ "f"),
    Nr = as.numeric(Nr)
  ) %>% 
  filter(!is.na(Nr)) %>%
  select(-Paras)
  

```

In this case, we combine station 5b with station 6     
* *Not* combining 5b with 5, as we did for intersex in L. littorea    
* For Figure 4  
* Used in part 7  


```{r}

dat_imposex_reticul <- readRDS("Data/02_Nettsnegl_intersex_2007_2014.RData") %>%
  bind_rows(df_2013)

# Some tables
if (FALSE){
  table(addNA(dat_imposex_reticul$Sex))
  table(addNA(dat_imposex_reticul$Station))
  table(addNA(dat_imposex_reticul$Station), addNA(dat_imposex_reticul$Year))
  xtabs(~addNA(stage) + Sex, dat_imposex_reticul)
}

dat_imposex_reticul_summ <- dat_imposex_reticul %>%
  mutate(Station = case_when(
    Station %in% "5b" ~ "6",
    Station != "5b" ~ Station)
    ) %>% # View()
  group_by(Station, Year) %>%
  summarize(VDSI = mean(stage, na.rm = TRUE),
            N_VDSI = sum(!is.na(stage)),
            SH = mean(SH, na.rm = TRUE),
            Pe_gl = mean(Pe_gl, na.rm = TRUE),
            .groups = "drop"
            ) %>%
  left_join(st_names, by = "Station")

# 1    4    5   5b    6    7
  
    # mutate(Station = case_when(Station %in% "St6" ~ "6",
    #                          TRUE ~ Station),
    #      Sex = case_when(tolower(Sex) %in% "f" ~ "f",
    #                      tolower(Sex) %in% "m" ~ "m",
    #                      TRUE ~ "x")
    #      )

df <- dat_imposex_reticul_summ %>%
  arrange(Year, Station ) %>%
  select(Station, Year, VDSI) %>%
  mutate(VDSI = round(VDSI, 2)) %>%
  pivot_wider(names_from = "Year", values_from = "VDSI") %>%
  arrange(desc(Station))

writexl::write_xlsx(df,  "Output_excel/06_Imposex_nettsnegl.xlsx")

df


```





## 2. TBT - tables of species
```{r}
xtabs(~Species, dat_tbt_mean)
xtabs(~Species + Year, dat_tbt_mean)

```

## 3. Littorina data
### a1. Chemical data  
```{r}
# xtabs(~Station + df_name, dat_tbt %>% filter(Species %in% "Littorina"))
xtabs(~Station + Year, dat_tbt %>% filter(Species %in% "Littorina"))

tab_tbt <- dat_tbt_mean_snails %>%
  group_by(Station, Year) %>%
  spread(Year, TBT_mean) %>%
  arrange(Species, desc(Station))

tab_tbt
```

### a2. Save TBT data to excel
```{r}

if (save_plots){
  
  writexl::write_xlsx(list(
    TBT = tab_tbt,
    Info = data.frame(Source = "Imposex_Littorina_Vikkilen script 06 (original filename: 06_Mean_tbt.xlsx)")
  ),
  "Output_excel/06_Mean_tbt.xlsx")

  # wb <- openxlsx::createWorkbook("DHJ")
  # openxlsx::addWorksheet(wb, "Littorina TBT")
  # openxlsx::writeData(wb, sheet = 1, tab_tbt)
  # openxlsx::saveWorkbook(wb, "Figures/06_Littorina_tables.xlsx", overwrite = TRUE)
}
```


### b. Intersex data, show tables  
```{r}

dat_intersex_litt %>%
  count(Sex, Female, Male)

dat_intersex_litt %>%
  count(Station, Year, Sex) %>%
  spread(Sex, n)

```

### c1a. Mean intersex per station/year, and add TBT  
dat_intersex_litt_summ 

- percentage sterile females (%S) = (number of sterile females/total number of females)*100  
    - stage 2-4 females are sterile  
- mean Female Penis Length (FPL)  
- mean Male Penis Length (MPL)  
- For N. lapillus,  
    - Relative Penis Size Index (RPSI) = (FPL)3/(MPL)3*100   
- imposex index (VDSI) = (sum of the values of imposex stages (ranged 0 to 5) in all females/the number of females collected)  
  
16 April 2020: 
- Combine 5 and 5B
```{r}

dat_intersex_litt_summ <- dat_intersex_litt %>%
  ungroup() %>%
  filter(Sex %in% "f") %>%
  mutate(Station = case_when(
    Station %in% "5b" ~ "5",
    Station != "5b" ~ Station),
    PRL = case_when(
      is.na(PRL) ~ 0,
      !is.na(PRL) ~ PRL),
    ISI = case_when(
      is.na(ISI) ~ 0,
      !is.na(ISI) ~ ISI)
    ) %>% # View()
  group_by(Station, Year) %>%
  summarize(ISI_mean = mean(ISI, na.rm = FALSE),
            N_ISI = sum(!is.na(ISI)),
            Sterile_perc = mean((ISI >= 2)*100, na.rm = TRUE),
            I_perc = mean((ISI > 0)*100, na.rm = TRUE),
            PRL_mean = mean(PRL, na.rm = FALSE),
            .groups = "drop"
            ) %>%
  ungroup()

nrow(dat_intersex_litt_summ)

#
# Add 2021 data
# NOT NEEDED - ALREADY ADDED IN c2!
""
# Only zeros 
# - taken from 2021 report 7701-2022, page 34, table 20
#
# check <- dat_intersex_litt_summ$Year == 2021
# 
# if (sum(check) == 0){
#   dat_intersex_litt_summ <- bind_rows(
#     dat_intersex_litt_summ,
#     tibble(
#       Station = c("1","4","6","7"),
#       Year = 2021,
#       ISI_mean = 0,
#       N_ISI = 50,
#       Sterile_perc = 0,
#       I_perc = 0,
#       PRL_mean = 0
#     )
#   )
# }



# Add TBT_mean, TBT_flag
dat_intersex_litt_summ <- dat_intersex_litt_summ %>%
  left_join(dat_tbt_mean_snails %>% 
              filter(Species %in% "Littorina") %>%
              ungroup() %>%
              select(Station, Year, TBT_mean, TBT_flag), 
            by = c("Station", "Year")
            )

# Check
# dat_intersex_litt_summ %>% arrange(Year) %>% tail(20)

nrow(dat_intersex_litt_summ)

```
### c1b. Add 71G data  
```{r}

dat_71G <- readxl::read_excel("Oppdatering sept2020/06_Littorina_tables_MSC.xlsx", sheet = "71G for R")

dat_intersex_litt_summ <- dat_intersex_litt_summ %>%
  bind_rows(dat_71G) %>%
  mutate(Sex = "f")


```

### c2. Add 2021 data   

* Data only given in Mail from Lise 25.5.2021 (forwarded from Merete 31.05)  
    - Data from four stations collected, Intersex = 0 for all  
    - st. 7 'Vikkilen innerst' and st 4 (hasseldalen) collected 5.5.2021  
    - st 1 Håøya and st. 6 Nymo collected 16.5.2021   
    - TBT not analysed yet (checked using '03_Check_chemistry_data_update2021.R')      
```{r}

if (FALSE){
  
  dat_intersex_litt_summ %>%
    filter(!is.na(ISI_mean)) %>%
    xtabs(~Year + Station, .)  
  
  dat_intersex_litt_summ %>%
    filter(Year == 2018)  
}

dat_extra <- data.frame(
  Year = rep(2021, 4),
  Station = c("1", "4", "6", "7"),
  Sex = "f",
  ISI_mean = rep(0, 4),
  Sterile_perc = rep(0, 4),
  I_perc = rep(0, 4),
  PRL_mean = rep(0, 4)
)  

# Check if there already are 2021 data  
check <- sum(dat_intersex_litt_summ$Year == 2021)
check

if (check == 0){
  dat_intersex_litt_summ <- bind_rows(
    dat_intersex_litt_summ,
    dat_extra
  )
}


```


### c3. Add station names  
```{r}


dat_intersex_litt_summ <- dat_intersex_litt_summ %>%
  left_join(st_names, by = "Station")


# str(dat_intersex_litt_summ)
# dat_intersex_litt_summ$Station


```

### c4. Save intersex data to excel
Add to existing 'wb' excel workbook  
```{r}

if (save_plots){
  
  # wb <- openxlsx::createWorkbook("DHJ")
  # openxlsx::addWorksheet(wb, "Littorina ISI raw")
  # openxlsx::writeData(wb, sheet = "Littorina ISI raw", dat_intersex_litt)
  # openxlsx::addWorksheet(wb, "Littorina ISI summ")
  # openxlsx::writeData(wb, sheet = "Littorina ISI summ", dat_intersex_litt_summ)
  
  tab1 <- dat_intersex_litt_summ %>%
    select(Station, Station_name, Station_name2, Year, ISI_mean) %>%
    pivot_wider(names_from = Year, values_from = ISI_mean, names_sort = TRUE) %>%
    arrange(desc(Station))

  tab2a <- dat_intersex_litt_summ %>%
    select(Station, Station_name, Station_name2, Year, I_perc) %>%
    mutate(I_perc = round(I_perc, 1)) %>%
    pivot_wider(names_from = Year, values_from = I_perc, names_sort = TRUE) %>%
    arrange(desc(Station))

  tab2b <- dat_intersex_litt_summ %>%
    select(Station, Station_name, Station_name2, Year, Sterile_perc) %>%
    pivot_wider(names_from = Year, values_from = Sterile_perc, names_sort = TRUE) %>%
    arrange(desc(Station))

  tab3 <- dat_intersex_litt_summ %>%
    select(Station, Station_name, Station_name2, Year, PRL_mean) %>%
    pivot_wider(names_from = Year, values_from = PRL_mean, names_sort = TRUE) %>%
    arrange(desc(Station))

  tab4 <- dat_intersex_litt_summ %>%
    select(Station, Station_name, Station_name2, Year, TBT_mean, TBT_flag) %>%
    mutate(TBT = case_when(
      is.na(TBT_flag) ~ as.character(TBT_mean),
      TBT_flag == 0 ~ as.character(TBT_mean),
      TBT_flag == 1 ~ paste("<", TBT_mean))
    ) %>%
    select(-TBT_mean, -TBT_flag) %>%
    pivot_wider(names_from = Year, values_from = TBT, names_sort = TRUE)  %>%
    arrange(desc(Station))

  writexl::write_xlsx(list(
    ISI = tab1,
    I_perc = tab2a,
    Sterile_perc = tab2b,
    PRL_mean = tab3,
    TBT = tab4,
    Info = data.frame(Source = "Imposex_Littorina_Vikkilen script 06 (original filename: 06_Means_Littorina.xlsx)")
  ),
  "Output_excel/06_Means_Littorina.xlsx")

}

```



### d1. Overview tables of mean values
```{r}

tab_ISI <- dat_intersex_litt_summ %>%
  mutate(ISI_mean = round(ISI_mean, 2)) %>%
  select(Station, Year, ISI_mean) %>%
  spread(Year, ISI_mean)
tab_ISI

tab_PRL <- dat_intersex_litt_summ %>%
  mutate(PRL_mean = round(PRL_mean, 2)) %>%
  select(Station, Year, PRL_mean) %>%
  filter(!is.na(PRL_mean)) %>%
  spread(Year, PRL_mean)
tab_PRL

tab_sterile <- dat_intersex_litt_summ %>%
  mutate(Sterile_perc = round(Sterile_perc, 1)) %>%
  select(Station, Year, Sterile_perc) %>%
  filter(!is.na(Sterile_perc)) %>%
  spread(Year, Sterile_perc)
tab_sterile

dat_intersex_litt_summ %>%
  mutate(PRL_mean = round(PRL_mean, 2)) %>%
  select(Station, Year, Sex, PRL_mean) %>%
  spread(Sex, PRL_mean)

tab_tbt
```

### d2. Save summary tables to excel  
```{r}

if (save_plots){
  
  wb <- openxlsx::createWorkbook("DHJ")
  openxlsx::addWorksheet(wb, "Littorina ISI")
  openxlsx::writeData(wb, sheet = "Littorina ISI", tab_ISI)
  openxlsx::addWorksheet(wb, "Littorina sterile")
  openxlsx::writeData(wb, sheet = "Littorina sterile", tab_ISI)
  openxlsx::addWorksheet(wb, "Littorina PRL")
  openxlsx::writeData(wb, sheet = "Littorina PRL", tab_PRL)
  openxlsx::saveWorkbook(wb, "Figures/06_Littorina_tables.xlsx", overwrite = TRUE)
}

```



## 4. Figure 2 and 3

* ISI + TBT
* ISI + VDSI
* Fig. 2 (old 2a) VDSI + TBT for Littorina (strandsnegl)        
    - section 7, 'Plot ISI + TBT, B/W'     
* Fig. 3 VDSI + TBT for Nassarius reticulatus (nettsnegl)
    - time series for VDSI (N. reticulatus) overlaid with ISI (for Littorina)   
    - section 7, 'Plot ISI + VDSI, B/W'   

### Littorina data for plotting ISI     
Just copy-paste from above  
```{r}

# 3. Combined figures for time series  

sts <- unique(dat_intersex_litt_summ$Station)
# df_pred_list <- sts %>% lapply(pred_logistic_from_stationname, variable = "ISI_mean")
df_pred_list <- sts %>% lapply(pred_logistic_from_stationname, variable = "ISI_mean",
                               data = dat_intersex_litt_summ, last_year=last_year)
# table(dat_intersex_litt_summ$Station)
# sts
names(df_pred_list) <- sts
# df_pred_list[["5b"]]

# Collect data for plotting 
df_pred_isi <- bind_rows(transpose(df_pred_list)$fit)
df_pvalue_isi <- bind_rows(transpose(df_pred_list)$pvalue)
df_points_isi <- dat_intersex_litt_summ %>% filter(!is.na(ISI_mean))

# Plot
if (FALSE){
  ggplot() + 
    geom_ribbon(data = df_pred_isi, 
                aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
    geom_path(data = df_pred_isi, 
              aes(x, y = Pred)) +
    geom_point(data = df_points_isi, 
               aes(Year, ISI_mean)) +
    geom_text(data = df_pvalue_isi, 
              aes(x = last_year, y = Inf, label = paste("ISI:", Text)), 
              vjust = 1.2, hjust = 1) +
    facet_wrap(vars(Station_name))
}

```

### Littorina data for plotting TBT     
As above but we change the curve to 'flat' for stations where tie trend pvalue > 0.05     

```{r}

sts_tbt <- dat_intersex_litt_summ %>%
  ungroup() %>%
  filter(!is.na(TBT_mean)) %>%
  count(Station) %>%
  filter(n >= 3) %>%
  pull(Station)

```


* Get tbt trend lines (df_pred_list) and P-values  
```{r}

# debugonce(pred_logistic_from_stationname)
df_pred_list <- sts_tbt %>% lapply(pred_logistic_from_stationname, 
                                   variable = "TBT_mean",
                                   data = dat_intersex_litt_summ,
                                   last_year=last_year)
names(df_pred_list) <- sts_tbt

# Get p-values for plot
df_pvalue_tbt <- bind_rows(transpose(df_pred_list)$pvalue)

# Check p-values
transpose(df_pred_list)$pvalue %>% bind_rows()

# For these three stations with pvalue > 0.20, so we use a flat line instead for these
# (df_pvalue_tbt is not updated, it is still used for printing p-value)
for (st in c("71G", "5","6"))
  df_pred_list[[st]] <- pred_flat_from_stationname(st, "TBT_mean")

# Collect data for plotting 
df_pred_tbt <- bind_rows(transpose(df_pred_list)$fit)
df_points_tbt <- dat_intersex_litt_summ %>% filter(!is.na(TBT_mean))

# Test plot
if (FALSE) {
  gg <- ggplot() + 
    geom_ribbon(data = df_pred_tbt, 
                aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
    geom_path(data = df_pred_tbt, aes(x, y = Pred)) +
    geom_point(data = df_points_tbt, 
               aes(Year, TBT_mean)) +
    geom_text(data = df_pvalue_tbt, aes(x = last_year, y = Inf, label = paste("TBT:", Text)), 
              vjust = 3.2, hjust = 1) +
    facet_wrap(vars(Station_name)) +
    labs(title = "TBT", x = "Year", y = "TBT concentration")
  gg
  
}

```


### FIG. 2 Plot ISI + TBT, B/W  

* Fig. 2 in paper

```{r, fig.width=7, fig.height=5}

# For transformation of TBT
ylim.prim <- c(0, 3.5)     # ISI
ylim.sec <- c(0, 510)    # TBT
b <- diff(ylim.prim)/diff(ylim.sec)
a <- b*(ylim.prim[1] - ylim.sec[1])


# nchar("Outer Vikkilen (2.5 km)") 
# 23 characters, let's breeak label when lines are longer than this

# Colors

# df_pred_isi <- df_pred_isi %>%
#   mutate(Station_name = fct_recode(
#     Station_name,
#     `Reference station\nLangesundfjord (100 km)` = "Reference station Langesundfjord (100 km)"
#   )
#   )
# 
# df_pred_tbt <- df_pred_tbt %>%
#   mutate(Station_name = fct_recode(
#     Station_name,
#     `Reference station\nLangesundfjord (100 km)` = "Reference station Langesundfjord (100 km)"
#   )
#   )


cols2 <- c("black", "black")

gg <- ggplot() + 
  # ISI data
  geom_ribbon(data = df_pred_isi, aes(x, ymin = Pred_lo, ymax = Pred_hi), 
              fill = "grey70", alpha = 0.5) +
  geom_path(data = df_pred_isi, aes(x, y = Pred), color = cols2[1]) +
  geom_point(data = df_points_isi, aes(Year, ISI_mean), color = cols2[1]) +
  # TBT data
  geom_ribbon(data = df_pred_tbt, aes(x, ymin = a + b*Pred_lo, ymax = a + b*Pred_hi), 
              fill = "grey70", alpha = 0.5) +
  geom_path(data = df_pred_tbt, aes(x, y = a + b*Pred), color = cols2[2],
            linetype = 2) +
  geom_point(data = df_points_isi, aes(Year, a + b*TBT_mean), color = cols2[2],
             shape = 2) +
  scale_y_continuous("ISI (circles)", 
                     sec.axis = sec_axis(~ (. - a)/b, name = "TBT μg/kg w.w. (triangles)")) +
  # P-values
    geom_text(data = df_pvalue_isi, aes(x = last_year, y = Inf, label = paste("ISI:", Text)), 
              vjust = 1.4, hjust = 1, size = 3.4) +
    geom_text(data = df_pvalue_tbt, aes(x = last_year, y = Inf, label = paste("TBT:", Text)), 
              vjust = 3.0, hjust = 1, size = 3.4) +
  # X axis
  geom_hline(yintercept = 0) +
  # Vertical dashed line 
  geom_vline(xintercept = c(2008), color = "red2", linetype = 2) +
  facet_wrap(vars(Station_name)) +      # labeller = label_wrap_gen(width = 28)
  labs(x = "Year") + 
  theme_bw() +
    theme(
        panel.grid = element_blank(),
        axis.line.y.left = element_line(color = cols2[1]), 
        axis.ticks.y.left = element_line(color = cols2[1]),
        axis.text.y.left = element_text(color = cols2[1]), 
        axis.title.y.left = element_text(color = cols2[1], vjust = 1.5),
        axis.line.y.right = element_line(color = cols2[2]), 
        axis.ticks.y.right = element_line(color = cols2[2]),
        axis.text.y.right = element_text(color = cols2[2]), 
        axis.title.y.right = element_text(color = cols2[2], vjust = 2)
        )

if (save_plots){
  ggsave("Figures/06_Timeseries_Comb_ISI_TBT_bw_FIG2.png", gg,
         width = 7, height = 5, dpi = 500)
  ggsave("Figures/06_Timeseries_Comb_ISI_TBT_bw_FIG2.svg", gg,
         width = 7, height = 5, dpi = 500)
}

gg

```




### Reticulata data for plotting VDSI  
```{r}

# Test for one station
if (FALSE){
  # From last chunk:
  x <- pred_logistic_from_stationname("1", variable = "TBT_mean", 
                                      data = dat_intersex_litt_summ, 
                                      last_year=last_year)
  str(x, 1)  
  # We just replace variable and data:
  x <- pred_logistic_from_stationname("1", variable = "VDSI", 
                                      data = dat_imposex_reticul_summ,
                                      last_year=last_year)
  str(x, 1)  
  
}

# Stations
sts_vdsi <- unique(dat_imposex_reticul_summ$Station)
# debugonce(pred_logistic_from_stationname)
df_pred_list <- sts_vdsi %>% 
  lapply(pred_logistic_from_stationname, 
         variable = "VDSI", 
         data = dat_imposex_reticul_summ, 
         last_year=last_year)
names(df_pred_list) <- sts_vdsi

# Get p-values for plot
df_pvalue_vdsi <- bind_rows(transpose(df_pred_list)$pvalue)

# Check p-values
transpose(df_pred_list)$pvalue %>% bind_rows()

# For this station with pvalue > 0.05, so we use a flat line instead for these:
# for (st in c("6"))
#   df_pred_list[[st]] <- pred_flat_from_stationname(st, 
#                                                    variable = "VDSI",
#                                                    data = dat_imposex_reticul_summ)

# Collect data for plotting 
df_pred_vdsi <- bind_rows(transpose(df_pred_list)$fit)
df_points_vdsi <- dat_imposex_reticul_summ %>% filter(!is.na(VDSI))

# Delete predictions after 2015, and before 2009 for some stations  
df_pred_vdsi <- df_pred_vdsi %>%
  filter(x <= 2016) %>%
  filter(!(x <= 2009 & Station %in% c("1","5")))

# Test plot
if (FALSE) {
  gg <- ggplot() + 
    geom_ribbon(data = df_pred_vdsi, 
                aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
    geom_path(data = df_pred_vdsi, aes(x, y = Pred)) +
    geom_point(data = df_points_vdsi, aes(Year, VDSI)) +
    geom_text(data = df_pvalue_vdsi, 
              aes(x = last_year, y = Inf, label = paste("VDSI:", Text)), 
              vjust = 3.2, hjust = 1) +
    facet_wrap(vars(Station_name)) +
    labs(title = "VDSI", x = "Year", y = "VDSI concentration") +
    coord_cartesian(ylim = c(0, 5.5))
  gg
  
}


```

### Reticulata data for plotting TBT     

* Get data  
```{r}

# Check 
# table(dat_tbt_mean_snails$Species)

dat_tbt_reticul_summ <- dat_tbt_mean_snails %>% 
  filter(Species %in% "Nassarius") %>%
  ungroup() %>%
  select(Station, Year, TBT_mean, TBT_flag)%>%
  left_join(st_names, by = "Station")
  

sts_tbt <- dat_tbt_reticul_summ %>%
  count(Station) %>%
  filter(n >= 3) %>%
  pull(Station)

# Check 
xtabs(~Year + Station, dat_tbt_reticul_summ)

```


* Get tbt trend lines (df_pred_list) and P-values  
```{r}

# debugonce(pred_logistic_from_stationname)
df_pred_list <- sts_tbt %>% lapply(pred_logistic_from_stationname, 
                                   variable = "TBT_mean",
                                   data = dat_tbt_reticul_summ,
                                   last_year=last_year)
names(df_pred_list) <- sts_tbt

# Get p-values for plot
df_pvalue_tbt <- bind_rows(transpose(df_pred_list)$pvalue)

# Check p-values
transpose(df_pred_list)$pvalue %>% bind_rows()

# For these three stations with pvalue > 0.20, so we use a flat line instead for these
# (df_pvalue_tbt is not updated, it is still used for printing p-value)
for (st in c("7", "5","6"))
  df_pred_list[[st]] <- pred_flat_from_stationname(st, 
                                                   variable = "TBT_mean",
                                                   data = dat_tbt_reticul_summ)

# Collect data for plotting 
df_pred_tbt <- bind_rows(transpose(df_pred_list)$fit)
df_points_tbt <- dat_tbt_reticul_summ %>% filter(!is.na(TBT_mean))

# Test plot
if (FALSE) {
  gg <- ggplot() + 
    geom_ribbon(data = df_pred_tbt, 
                aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
    geom_path(data = df_pred_tbt, aes(x, y = Pred)) +
    geom_point(data = df_points_tbt, 
               aes(Year, TBT_mean)) +
    geom_text(data = df_pvalue_tbt, 
              aes(x = last_year, y = Inf, label = paste("TBT:", Text)), 
              vjust = 3.2, hjust = 1) +
    facet_wrap(vars(Station_name)) +
    labs(title = "TBT", x = "Year", y = "TBT concentration")
  gg
  
}

```

### FIG. 3. TBT + VDSI, VDSI on left (not right) axis 
```{r}

# For transformation of TBT
ylim.prim <- c(0, 5.5)     # ISI
ylim.sec <- c(0, 510)    # TBT
b <- diff(ylim.prim)/diff(ylim.sec)
a <- b*(ylim.prim[1] - ylim.sec[1])

gg <- ggplot() + 
  # VDSI trends
  geom_ribbon(data = df_pred_vdsi, aes(x, ymin = Pred_lo, ymax = Pred_hi), 
              fill = "grey70", alpha = 0.5) +
  geom_path(data = df_pred_vdsi, aes(x, y = Pred), color = cols2[1]) +
  # X axis
  geom_hline(yintercept = 0) +
  # Vertical dashed line 
  geom_vline(xintercept = c(2008), color = "red2", linetype = 2) +
  facet_wrap(vars(Station_name)) +      # labeller = label_wrap_gen(width = 28)
  labs(x = "Year") + 
  theme_bw() +
    theme(
        panel.grid = element_blank(),
        axis.line.y.left = element_line(color = cols2[1]), 
        axis.ticks.y.left = element_line(color = cols2[1]),
        axis.text.y.left = element_text(color = cols2[1]), 
        axis.title.y.left = element_text(color = cols2[1], vjust = 1.5),
        axis.line.y.right = element_line(color = cols2[2]), 
        axis.ticks.y.right = element_line(color = cols2[2]),
        axis.text.y.right = element_text(color = cols2[2]), 
        axis.title.y.right = element_text(color = cols2[2], vjust = 2)
        )

# VDSI points
gg <- gg +
   geom_point(data = dat_imposex_reticul_summ, aes(Year, VDSI), color = cols2[1]) 
  
# TBT trends  
gg <- gg +
  geom_ribbon(data = df_pred_tbt, aes(x, ymin = a + b*Pred_lo, ymax = a + b*Pred_hi), 
              fill = "grey70", alpha = 0.5) +
  geom_path(data = df_pred_tbt, aes(x, y = a + b*Pred), color = cols2[2],
            linetype = 2)

# TBT points 
gg <- gg +
  geom_point(data = df_points_tbt, aes(Year, a + b*TBT_mean), color = cols2[2],
             shape = 2) +
  scale_y_continuous("VDSI (circles)", 
                     sec.axis = sec_axis(~ (. - a)/b, name = "TBT μg/kg w.w. (triangles)"))

# P-values
gg <- gg +
    geom_text(data = df_pvalue_vdsi, aes(x = last_year, y = Inf, label = paste("ISI:", Text)), 
              vjust = 1.4, hjust = 1, size = 3.4) +
    geom_text(data = df_pvalue_tbt, aes(x = last_year, y = Inf, label = paste("TBT:", Text)), 
              vjust = 3.0, hjust = 1, size = 3.4)

# Adjust y scale
gg <- gg +
    coord_cartesian(ylim = c(0, 5.5))
  

if (save_plots){
  ggsave("Figures/06_Timeseries_Comb_TBT_VDSI_bw_FIG3.png", gg,
         width = 7, height = 5, dpi = 500)
  ggsave("Figures/06_Timeseries_Comb_TBT_VDSI_bw_FIG3.svg", gg,
         width = 7, height = 5, dpi = 500)
}


gg

```



## 5. Figure 4

```{r}

## Was: 6. Littorina plots using logistic function   

```

```{r}
source("06_Tables_graphs_functions.R")
```



### Plot PRL at all stations  

* Fig. 4     

```{r}
# back <- dat_intersex_litt_summ

# dat_intersex_litt_summ <- dat_intersex_litt_summ %>%
#   mutate(Station2 = )

# We make regressions for only two stations
sts <- c("5", "6", "7")
# debugonce(pred_logistic_from_stationname)
df_pred_list <- sts %>% lapply(pred_logistic_from_stationname, variable = "PRL_mean", last_year=last_year)
names(df_pred_list) <- sts
# df_pred_list[["5b"]]

# Collect data for plotting 
df_pred <- bind_rows(transpose(df_pred_list)$fit)
df_pvalue <- bind_rows(transpose(df_pred_list)$pvalue)
df <- dat_intersex_litt_summ %>% filter(!is.na(PRL_mean))

# Plot
gg <- ggplot() + 
  geom_ribbon(data = df_pred, aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
  geom_path(data = df_pred, aes(x, y = Pred)) +
  geom_point(data = df, aes(Year, PRL_mean)) +
  geom_text(data = df_pvalue, aes(x = last_year, y = Inf, label = Text), 
            vjust = 1.2, hjust = 1, size = 3.4) +
  geom_vline(xintercept = c(2008), color = "red2", linetype = 2) +
  facet_wrap(vars(Station_name)) +
  labs(x = "Year", y = "FPrL") +
  geom_hline(yintercept = 0) +
  theme_bw() +
  theme(panel.grid = element_blank())
if (save_plots)
  ggsave("Figures/06_Timeseries_Litt_PRL_FIG4.png", gg,
         width = 6, height = 4, dpi = 500)
gg


```

## 6. Figure 5  

  ### Combined plot  

```{r, fig.height = 7, fig.width= 9}


plot_margins <- c(0.2, 0.3, 0.5, 0.7)  # top, right, bottom, left

gg_a_withlegend <- ggplot(dat_intersex_litt_summ, aes(TBT_mean, ISI_mean)) +
  geom_smooth(method = "lm", formula = 'y ~ x', color = "black") +
  labs(x = "TBT (μg/kg w.w.)", y = "ISI") +
  geom_point(aes(fill = Station_name), pch = 21, size = rel(2)) +
  scale_fill_manual("", values = station_cols)

gg_a <- gg_a_withlegend +
  theme_bw() +
  theme(legend.position="none", 
        plot.margin = unit(plot_margins, "cm"),
        panel.grid = element_blank())

gg_b <- ggplot(dat_intersex_litt_summ, aes(PRL_mean, ISI_mean)) +
  geom_smooth(method = "lm", formula = 'y ~ x', color = "black") +
  labs(x = "FPrL", y = "ISI") +
  geom_point(aes(fill = Station_name), pch = 21, size = rel(2)) +
  scale_fill_manual("", values = station_cols) +
  theme_bw() +
  theme(legend.position="none", 
        plot.margin = unit(plot_margins, "cm"),
        panel.grid = element_blank())

gg_c <- ggplot(dat_intersex_litt_summ, aes(TBT_mean, PRL_mean)) +
  geom_smooth(method = "lm", formula = 'y ~ x', color = "black") +
  labs(x = "TBT (μg/kg w.w.)", y = "FPrL") +
  geom_point(aes(fill = Station_name), pch = 21, size = rel(2)) +
  scale_fill_manual("", values = station_cols) +
  theme_bw() +
  theme(legend.position="none", 
        plot.margin = unit(plot_margins, "cm"),
        panel.grid = element_blank())

gg_d <- ggplot(dat_intersex_litt_summ, aes(ISI_mean, Sterile_perc)) +
  geom_smooth(method = "lm", formula = 'y ~ x', color = "black") +
  labs(x = "ISI", y = "Percentage sterile females (%)") +
  geom_point(aes(fill = Station_name), pch = 21, size = rel(2)) +
  scale_fill_manual("", values = station_cols) +
  theme_bw() +
  theme(legend.position="none", 
        plot.margin = unit(plot_margins, "cm"),
        panel.grid = element_blank())

legend <- cowplot::get_legend(gg_a_withlegend)

gg_comb <- cowplot::plot_grid(gg_a, gg_b, NULL, gg_c, gg_d, legend,
                   labels = c("A", "B", NA, "C", "D", NA), 
                   nrow = 2, rel_widths = c(1, 1, .6))


if (save_plots)
  ggsave("Figures/06_Correlations_combined_color_FIG5.png", gg_comb,
         width = 7.8, height = 5.8, dpi = 500)

gg_comb

```


### Correlations
```{r, fig.height = 5, fig.width=6}

print_correlations <- function(){
  
  cat("=================================\nCorrelation TBT_mean, ISI_mean \n\n")
  with(dat_intersex_litt_summ, cor.test(TBT_mean, ISI_mean, method = "kendall")) %>% print()
  
  cat("=================================\nCorrelation TBT_mean, PRL_mean \n\n")
  with(dat_intersex_litt_summ, cor.test(TBT_mean, PRL_mean, method = "kendall")) %>% print()
  
  cat("=================================\nCorrelation PRL_mean, ISI_mean \n\n")
  with(dat_intersex_litt_summ, cor.test(PRL_mean, ISI_mean, method = "kendall")) %>% print()
  
  cat("=================================\nCorrelation Sterile_perc, ISI_mean \n\n")
  with(dat_intersex_litt_summ, cor.test(Sterile_perc, ISI_mean, method = "kendall")) %>% print()
  
}

# Print to file
fn <- "Figures/06_Kendall_correlations.txt"
con <- file(fn, open = "w")
sink(con)
print_correlations()
sink()
close(con)

# Show file
# file.show(fn)

# Print to result
cat("\n")
print_correlations()

```
