---
title: "07_New_data_July2020"
author: "DHJ"
date: "8 7 2020"
output: html_document
---

Figures in MS:
* 7A (graph)   
    - Section 6 PLot TBT - "In same format as rest"   
    - '07_tbt_vs_year_FIG7A.png'  
* 7B (map) edited based on map from 3b - "bathymetry with sample positions"   
    - Section 3b "Bathymetry with samples I", creates 'Areas3c.jpg'    
    - Areas3c_edit2 (Areas3c, but manually edited in Paint)

```{r setup}

library(ggplot2)
library(dplyr)
library(readxl)

library(leaflet)

```

## 1. Data
Data 'dat' defined  


### Read data from excel    
```{r data}

dat <- read_excel("Input_data/kartfil sediment.xlsx") %>%
  mutate(
    # Convert text to numeric
    #   e.g. text "<0,602" to numeric 0.0602
    TBT = 
      sub(",", ".", `TBT (µg/kg TS)`) %>%
      sub("<", "", .) %>%
      as.numeric(),
    # Make "Flag" variable (presence of "<")
    Flag = case_when(
      grepl("<", `TBT (µg/kg TS)`) ~ "<",
      TRUE ~ as.character(NA))
  )
colnames(dat)[2] <- "Year"
colnames(dat)[3] <- "Date"
colnames(dat)[7] <- "Long"
colnames(dat)[8] <- "Lat"

# dat

xtabs(~addNA(Year), dat)

# Keep rows with year given  
dat <- dat %>%
  filter(!is.na(Year))

# Add row number
dat <- dat %>%
  mutate(i = 1:nrow(dat))

head(dat)

```
### Add column for colors per year    
Used in plot later
```{r}

years <- dat$Year %>% unique()

# Just a few possible colors can be used in leaflet.
#   See ?awesomeIcons for color list; I copy/pasted these colors from this help page  
# Make list the same length as 'years':  
cols <- c("red", "darkred", "lightred", "orange", "beige", "green", "darkgreen", "lightgreen", "blue")
lookup_colors <- data.frame(Year = years, Color = cols)
# dat$Color <- NULL
dat <- dat %>% 
  left_join(lookup_colors)

```

### Overlapping data from script 05?  
```{r}

dat_script05 <- readRDS(file = "Data/05_TBT.RData")

full_join(
  dat %>%
    distinct(Long, Lat, Year) %>%
    count(Year, name = "dat"),
  dat_script05 %>%
    filter(Species %in% "Sediment") %>%
    distinct(Station, Year) %>%
    count(Year, name = "dat_script05"), 
  by = "Year"
) %>%
  arrange(Year)


```

Check - seems to be ok
```{r}
get_stations <- function(year){
  cat(year, ":\n")
  dat %>%
    filter(Year == year) %>%
    distinct(stasjon) %>%
    pull(stasjon)  %>% paste(collapse = "; ") %>% cat("dat:", .)
  cat("\n")
  dat_script05 %>%
    filter(Species %in% "Sediment" & Year == year) %>%
    distinct(Station) %>%
    pull(Station) %>% paste(collapse = "; ") %>%cat("dat_script05:", .)
  cat("\n")
  
}

get_stations(2005)
cat("\n")
get_stations(2008)


```

## 2. Check area division in areas 
Lines for area division dividing inner part of the bay  

### Define dividing lines + wharf    
This chunk was run repeatedly, checking maps in section 3 and 4       
```{r}

# Northernmost horizontal line
lat2 <- 58.3602
df_line2 <- data.frame(
  Long = c(8.610, 8.625),
  Lat = rep(lat2,2)
)

# Middle horizontal line
lat3 <- 58.3555
df_line3 <- data.frame(
  Long = c(8.605, 8.622),
  Lat = rep(lat3, 2)
)

# Southernmost horizontal line
lat4 <- 58.33
df_line4 <- data.frame(
  Long = c(8.58, 8.622),
  Lat = rep(lat4, 2)
)

# Line dividing West/east parts  
df_line1 <- data.frame(
  Long = c(8.61228, 8.6152),
  Lat = c(lat3, 58.3630)
)

wharf_data <- matrix(c(
58.3568997,
8.6113226,
58.3581243,
8.61033,
58.3625255,
8.6118885,
58.3626917,
8.6104532,
58.3584945,
8.6089259,
58.3584243,
8.6096638,
58.3567816,
8.6099165), ncol = 2, byrow = TRUE)

coord_wharf <- cbind(X = wharf_data[,2], Y = wharf_data[,1], L1 = 1, L2 = 1)
coord_wharf
colnames(coord_wharf)[1:2] <- c("Y", "X")
# str(coord_wharf)


```

## 3a. Leaflet maps  

### Map center  
```{r}

map_center <- c(8.6070, 58.3494)

```


### Markers with colors for each year  
```{r}
# RColorBrewer::display.brewer.all()
leaf <- dat %>%
  leaflet() %>% 
  addTiles()

leaf %>%
  addPolylines(lng = df_line1$Long, df_line1$Lat) %>%
  addPolylines(lng = df_line2$Long, df_line2$Lat) %>%
  addPolylines(lng = df_line3$Long, df_line3$Lat) %>%
  addPolylines(lng = df_line4$Long, df_line4$Lat) %>%
  addLabelOnlyMarkers(lng = map_center[1], lat = map_center[2], label = "A",
                      labelOptions = labelOptions(
                        noHide = T, direction = 'top', textOnly = T,
                        textsize = "18px", 
                        style = list(
                          "color" = "blue",
                          "font-family" = "sans-serif",
                          "font-style" = "normal"
                          )
                      )
  )
# https://stackoverflow.com/questions/31745525/leaflet-with-r-add-text-labels
# https://rstudio.github.io/leaflet/popups.html
# 


```


### Markers with colors for each year  
```{r}
# RColorBrewer::display.brewer.all()

icons <- awesomeIcons(       # Function 2 is a "meta-function" 
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = dat$Color
)

leaf <- dat %>%
  leaflet() %>% 
  addTiles() %>% 
  addAwesomeMarkers(lng = ~Long, lat = ~Lat, icon = icons, 
                    label = ~paste(Year, paste0(Long, ", ", Lat), i, sep = "<br>") %>% 
                      purrr::map(htmltools::HTML))
leaf %>%
  addPolylines(lng = df_line1$Long, df_line1$Lat) %>%
  addPolylines(lng = df_line2$Long, df_line2$Lat) %>%
  addPolylines(lng = df_line3$Long, df_line3$Lat) %>%
  addPolylines(lng = df_line4$Long, df_line4$Lat)

```

### Map with smaller sample symbols  
```{r}

dat %>%
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~Long, lat = ~Lat, radius = 5, color = "red") %>%
  addPolylines(lng = df_line1$Long, df_line1$Lat) %>%
  addPolylines(lng = df_line2$Long, df_line2$Lat) %>%
  addPolylines(lng = df_line3$Long, df_line3$Lat) %>%
  addPolylines(lng = df_line4$Long, df_line4$Lat)


```




## 3b. Map using nivamaps (aerial photo ) 

```{r}
library(nivamaps)
library(sf)

df_lines <- list(df_line1, df_line2, df_line3, df_line4)

for (i in 1:4){
  df_lines[[i]] <-   data.frame( df_lines[[i]], L1 = 1, L2 = 1)
  df_lines[[i]] <- as.matrix(df_lines[[i]])
}

```

### Toporaster
```{r}
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
         height = 600, width = 600,
         layer = "no.norgedigitalt:toporaster") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  make_html("Figures/07_sediment_areas_01.html")

```

### Toporaster with points
```{r}

df_samples <- dat[,c("Lat","Long")] %>% as.matrix()
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
         height = 1100, width = 1100,
         layer = "no.norgedigitalt:toporaster") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_points(df_samples, radius = 3, color = "#ffad4f", border = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  make_html("Figures/07_sediment_areas_01_points.html")


```


### N250
```{r}
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
         height = 600, width = 600,
         layer = "no.niva:N250") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  make_html("Figures/07_sediment_areas_02.html")

```

### Aerial photo  
```{r}
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
         height = 600, width = 600,
         layer = "no.norgedigitalt:flyfoto") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  make_html("Figures/07_sediment_areas_03.html")
```


### Bathymetry with samples I    

* Fig. 6B    
* The map used is Areas3c_edit2 (Areas3c, but manually edited in Paint)

```{r}

df_samples <- dat[,c("Lat","Long")] %>% as.matrix()
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
         height = 1100, width = 1100,
         layer = "no.niva:Marin") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_points(df_samples, radius = 5, color = "#ffad4f", border = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  make_html("Figures/07_sediment_areas_04.html")

# Areas3 + 3b: height = 1100, width = 1100, radius = 3
# Areas3c: height = 1100, width = 1100, radius = 5

#
# Map layers that work:
#
# no.norgedigitalt:toporaster
# no.norgedigitalt:flyfoto
# no.norgedigitalt:N5000 (for larger areas / small zoom numbers)
# no.norgedigitalt:EuroFoto (for larger areas / for small zoom numbers)
# no.niva:N250 (a bit slow)
# no.niva:Marin (a bit slow)


```


### Bathymetry with samples II      

* Could also be used for fig. 6A map?  
* Note that position of letters depends a lot on zoom level (because they are only labels)    

```{r}

coor_letters <- matrix(c(
58.3620894,
8.6126317,
58.3626,
8.6172068,
58.3600,
8.61200,
58.3600,
8.6159,
58.3570,
8.60879), ncol = 2, byrow = TRUE)

lettersize <- 25

df_samples <- dat[,c("Lat","Long")] %>% as.matrix()
make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 16,
         height = 1100, width = 1100,
         layer = "no.niva:Marin") %>%
  add_polygon(data = coord_wharf, col_lat = 1, col_long = 2, 
              border_color = "black", fill = TRUE) %>%
  add_points(df_samples, radius = 5, color = "#ffad4f", border = TRUE) %>%
  add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8") %>%
  add_text(long = coor_letters[1,2], lat = coor_letters[1,1], label = "1", size = lettersize) %>%
  add_text(long = coor_letters[2,2], lat = coor_letters[2,1], label = "2", size = lettersize) %>%
  add_text(long = coor_letters[3,2], lat = coor_letters[3,1], label = "3", size = lettersize) %>%
  add_text(long = coor_letters[4,2], lat = coor_letters[4,1], label = "4", size = lettersize) %>%
  add_text(long = coor_letters[5,2], lat = coor_letters[5,1], label = "5", size = lettersize) %>%
  make_html("Figures/07_sediment_areas_04b.html")

# Areas3 + 3b: height = 1100, width = 1100, radius = 3
# Areas3c: height = 1100, width = 1100, radius = 5

#
# Map layers that work:
#
# no.norgedigitalt:toporaster
# no.norgedigitalt:flyfoto
# no.norgedigitalt:N5000 (for larger areas / small zoom numbers)
# no.norgedigitalt:EuroFoto (for larger areas / for small zoom numbers)
# no.niva:N250 (a bit slow)
# no.niva:Marin (a bit slow)


```




## 3c. Map using manulal copy/paste into HTML  

* Using the file '07_sediment_areas_manual.html'    
    - This file was based on `index_withMarker_singlefile.html`   
    - which again was based on https://github.com/kartverket/example-clients   
    - had to modify the javascript part (originally in `L.TileLayer.Kartverket.min.js`)   
    - chese changes were based on GetCapabilities, see Readme.txt in 'C:\Data\R_test\Leaflet-kartverket'  
* 



```{r}

library(nivamaps)
library(sf)

df_lines <- list(df_line1, df_line2, df_line3, df_line4)

for (i in 1:4){
  df_lines[[i]] <-   data.frame( df_lines[[i]], L1 = 1, L2 = 1)
  df_lines[[i]] <- as.matrix(df_lines[[i]])
}

```

### Modify nivamaps functions so they accept CRS  

```{r}

source("07_nivamaps_modified_functions.R")

```

### Make leaflet parts for copying  

* Using crs 3857 (pseudo-Mercator) - i.e. not transforming coordinates   
    - transform from 3857 to 3857    
* The leaflet parts of this (most of the file) were then added to '07_sediment_areas_manual.html' by copy-paste  
* Opened this in browser, selected background mal, copy-paste to powerpoint using Snip  
    - File 07_sediment_areas_manual.pptx  
    - then saved as png and copy-paste to word, see last page in the ppt

```{r}

  make_map(center_lon = map_center[1], center_lat = map_center[2], zoom = 14,
           height = 600, width = 600,
           layer = "no.norgedigitalt:toporaster") %>%
    add_polyline(data = df_lines[[1]], col_lat = 2, col_long = 1, border_color = "#377eb8", crs=3857) %>%
    add_polyline(data = df_lines[[2]], col_lat = 2, col_long = 1, border_color = "#377eb8", crs=3857) %>%
    add_polyline(data = df_lines[[3]], col_lat = 2, col_long = 1, border_color = "#377eb8", crs=3857) %>%
    add_polyline(data = df_lines[[4]], col_lat = 2, col_long = 1, border_color = "#377eb8", crs=3857) %>%
    add_points(df_samples, radius = 5, color = "#ffad4f", border = TRUE, crs=3857) %>%
    make_html("Figures/07_sediment_areas_manual_parts_for_copying.html")

```



## 4. Plot TNT levels spatially    
Check how they fit, redefine areas (section 2) if necessary  

### All years, all data  
```{r}

# RColorBrewer::display.brewer.all()

dat %>%
  ggplot(aes(Long, Lat)) +
  geom_point(aes(color = TBT)) +
  scale_color_distiller(palette = "Spectral") +
  facet_wrap(vars(Year)) +
  geom_path(data = df_line1 %>% mutate(Long = Long - 0.00)) +
  geom_path(data = df_line2) +
  geom_path(data = df_line3)


```

### All years, areas 1-5 (not 6)  
```{r}

# RColorBrewer::display.brewer.all()

dat %>%
  filter(Lat > lat4) %>%
  ggplot(aes(Long, Lat)) +
  geom_point(aes(color = TBT)) +
  scale_color_distiller(palette = "Spectral") +
  facet_wrap(vars(Year)) +
  geom_path(data = df_line1 %>% mutate(Long = Long - 0.00)) +
  geom_path(data = df_line2) +
  geom_path(data = df_line3)


```
### 2004  
```{r}

# RColorBrewer::display.brewer.all()

dat %>%
  filter(Lat > 58.335 & Year %in% c(2004,2008)) %>%
  ggplot(aes(Long, Lat)) +
  geom_point(aes(color = TBT)) +
  scale_color_distiller(palette = "Spectral") +
  facet_wrap(vars(Year), nrow = 1) +
  geom_path(data = df_line1 %>% mutate(Long = Long - 0.00)) +
  geom_path(data = df_line2) +
  geom_path(data = df_line3)

```

## 5. Define 'Area' column in data set  
- Based on the lines defined in section 3, first chink
- Data 'dat2'  
```{r}

# Function for finding whther a point is north of a line
# Returnes TRUE/FALSE
point_north_of_line <- function(long, lat, line){
  prop_x <- (long - line$Long[1])/diff(line$Long)
  slope <- diff(line$Lat)/diff(line$Long)
  y_on_line <- line$Lat[1] + slope*prop_x*diff(line$Long)
  lat > y_on_line
}
# TEst
 i <- 24
 point_north_of_line(dat$Long[i], dat$Lat[i], df_line3)
 i <- 33
 point_north_of_line(dat$Long[i], dat$Lat[i], df_line3)


# Define areas west/north of 'df_line1'  
# Mathematically we use 'point_north_of_line' to find it
dat$West_of_line <- 1:nrow(dat) %>% purrr::map_lgl(~point_north_of_line(dat$Long[.], dat$Lat[.], df_line1))

dat2 <- dat %>%
  mutate(
    Area = case_when(
      Lat > lat2 & West_of_line ~ 1,
      Lat > lat2 & !West_of_line ~ 2,
      Lat > lat3 & West_of_line ~ 3,
      Lat > lat3 & !West_of_line ~ 4,
      Lat > lat4 ~ 5,
      Lat <= lat4 ~ 6),
    LOQ = case_when(
      is.na(Flag) ~ "Over LOQ",
      !is.na(Flag) ~ "Under LOQ")
  )


xtabs(~Area + Year, dat2)

# PLots for checking that areas work  
if (FALSE){
  gg <- dat2 %>%
    ggplot(aes(Long, Lat)) +
    geom_point(aes(color = factor(Area))) +
    facet_wrap(vars(Year)) +
    geom_path(data = df_line1 %>% mutate(Long = Long - 0.00)) +
    geom_path(data = df_line2) +
    geom_path(data = df_line3)
  
  gg
  gg + coord_cartesian(ylim = c(58.35,58.37))
  
}


```

## 6. Plot TBT  

### Version 1  
```{r}

gg <- dat2 %>%
  ggplot(aes(Year, TBT)) +
  geom_point(aes(shape = LOQ)) +
  scale_shape_manual(values = c(19, 6))

gg + 
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(vars(Area))
gg + 
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(vars(Area), scales = "free_y")
gg + scale_y_log10() +
  geom_smooth(method = "lm") +
  facet_wrap(vars(Area))


```

### Version 2    
```{r}


gg <- dat2 %>%
  mutate(Area = factor(Area)) %>%
  ggplot(aes(Year, TBT, group = Area, color = Area)) +
  scale_color_manual(values = RColorBrewer::brewer.pal(5, "Set1")) + 
  geom_smooth(method = "lm") +
  scale_y_log10() +
  labs(y = "TBT (μg/kg d.w.)", x = "") +
  theme_bw() +
  theme(panel.grid = element_blank())

ggsave("Figures/07_tbt_vs_year_FIG7A.png", gg, 
         width = 4, height = 2.7, dpi = 500)

gg


```

## 7. Statistics  
### Regression table (for each area)  
```{r}
  
dat2 %>%
  split(.$Area) %>% 
  purrr::map(~lm(log(TBT) ~ Year, data = .), .id = "Area") %>%
  huxtable::huxreg()

```

### ANCOVA regression  
```{r}

m1 <- lm(log(TBT) ~ Year*factor(Area), data = dat2)
m2 <- lm(log(TBT) ~ Year + factor(Area), data = dat2)
m3 <- lm(log(TBT) ~ Year, data = dat2)
summary(m2)
anova(m1, m2, m3)

# Change per year, log-scale
slope <- summary(m2)$coef["Year", "Estimate"] 
slope_lo <- slope - 2*summary(m2)$coef["Year", "Std. Error"] 
slope_hi <- slope + 2*summary(m2)$coef["Year", "Std. Error"] 
# Change per year, translated to percent on the ordinary scale
perc_mid <- 100*(1 - exp(slope)) %>% round(3)
perc_lo <- 100*(1 - exp(slope_lo)) %>% round(3)
perc_hi <- 100*(1 - exp(slope_hi)) %>% round(3)
cat("Change per year: ", perc_mid, " % (C.I. ", perc_hi, " - ", perc_lo, "%)", sep = "")




```


### Logistic regression   
Same function as used in sript 06  

#### Plots type 'base plot'  
```{r}

source("06_Tables_graphs_functions.R")

plot_TBT_allareas <- function(data, ylim = NULL, add_pvalue = FALSE){
  
  par(mfrow = c(2,3), mar = c(4,5,2,1))
  for (area in 1:5){
    # area <- 1
    df <- data %>% filter(Area %in% area & !is.na(TBT))
    
    df_pred <- pred_logistic(df$Year, df$TBT, x_range = range(df$Year), a = 0.05)
    
    plot(TBT ~ Year, data = df, type = "n", xlab = "", ylab = "", 
         xlim = c(1994, 2016), ylim = ylim)
    with(df_pred$fit, polygon.lines(x, Pred_lo, Pred_hi, border = FALSE))
    with(df_pred$fit, lines(x, Pred))
    with(df, points(Year, TBT, pch = 19))
    mtext(paste("Area", area), line = 0.5)

    if (add_pvalue){
      pvalue <- summary(df_pred$model)$coef["x","Pr(>|t|)"] %>% round_pvalue_txt()
      text(1995, 90000, pvalue, adj = 0)
    } 
    
  }
  
}

# Different y scales
plot_TBT_allareas(dat2)

# Common y scale  
plot_TBT_allareas(dat2, ylim = c(0, max(dat2$TBT, na.rm = TRUE)), add_pvalue = TRUE)
# plot_TBT_allareas(dat2, ylim = c(0, max(dat2$TBT, na.rm = TRUE)), add_pvalue = FALSE)

```
#### In same format as rest - data for plotting
```{r}

get_TBT_pred <- function(area, data){
  
  par(mfrow = c(2,3), mar = c(4,5,2,1))
    # area <- 1
    df <- data %>% filter(Area %in% area & !is.na(TBT))
    
    df_pred <- pred_logistic(df$Year, df$TBT, x_range = range(df$Year), a = 0.05)
    
    p_value <- summary(df_pred$model)$coef["x","Pr(>|t|)"] %>% round_pvalue_txt()
    
    list(df_pred$fit, p_value)

}

# Test
# get_TBT_pred(1, dat2) %>% str(1)

# All areas
areas <- as.character(1:5)

result <- areas %>% map(get_TBT_pred, data = dat2) %>% set_names(areas)
result_t <- transpose(result)

# str(result_t)

df_pred <- result_t[[1]] %>% bind_rows(.id = "Area")
df_pvalue <- data.frame(
  Area = areas,
  Text = result_t[[2]] %>% unlist()
)


```

#### In same format as rest - plot   

* Fig. 6B  

```{r}

# Plot
gg <- ggplot() + 
  geom_ribbon(data = df_pred, aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
  geom_path(data = df_pred, aes(x, y = Pred)) +
  geom_point(data = dat2 %>% filter(Area < 6), aes(Year, TBT)) +
  geom_text(data = df_pvalue, aes(x = 1995, y = Inf, label = Text), 
            hjust = 0, vjust = 1, size = 3) +
  facet_wrap(vars(Area), labeller = "label_both") +
  labs(y = "TBT in sediment (μg/kg TS)")

if (save_plots){
  ggsave("Figures/07_tbt_vs_year_logistic_1.png", 
         gg,
         width = 8, height = 5, dpi = 500)
  ggsave("Figures/07_tbt_vs_year_logistic_2.png", 
         gg + scale_y_log10(),
         width = 8, height = 5, dpi = 500)
}

gg

gg + scale_y_log10()

```

### Plot percent sterile at all stations
```{r}
# Run all stations (as above)
sts <- dat2 %>% filter(!is.na(TBT)) %>% pull(Area) %>% unique()
debugonce(pred_logistic_from_stationname)
pred_logistic_from_stationname(
  1, variable = "TBT", data = dat2 %>% mutate(Station = as.character(Area)))

df_pred_list <- sts %>% lapply(pred_logistic_from_stationname, variable = "TBT", data = dat2)
names(df_pred_list) <- sts

# Check p-values
transpose(df_pred_list)$pvalue %>% bind_rows()

# Run 4 using linear regression
df_pred_list[["4"]] <- pred_linear_from_stationname("4", "Sterile_perc")

# Collect data for plotting 
df_pred <- bind_rows(transpose(df_pred_list)$fit)
df_pvalue <- bind_rows(transpose(df_pred_list)$pvalue)
df <- dat_intersex_litt_summ %>% filter(!is.na(Sterile_perc))

# Plot
gg <- ggplot() + 
  geom_ribbon(data = df_pred, aes(x, ymin = Pred_lo, ymax = Pred_hi), fill = "grey70") +
  geom_path(data = df_pred, aes(x, y = Pred)) +
  geom_point(data = df, aes(Year, Sterile_perc)) +
  geom_text(data = df_pvalue, aes(x = 2016, y = Inf, label = Text), vjust = 1.2) +
  facet_wrap(vars(Station_name)) +
  labs(title = "Percent of sterile females", x = "Year", y = "Percent sterile")
if (save_plots)
  ggsave("Figures/06_Timeseries_Litt_sterile.png", gg,
         width = 8, height = 5, dpi = 500)
gg

```
